An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/impl.tex
config: table 2
config: table
config: imple

The translator is developed as a parser for the grammar
described in $\S$\ref{sec-trans}. 
%The implementation presented no interesting challenges.

The learning and checking modules are developed to allow
for customized extensibility. In order to verify a configuration file
against a new type of error, a user only needs to provide a new type
that is an instance of the \textit{Attribute} typeclass (\ie, define some
functions over that type). 
In particular, for each type of error the users
wish to detect, they must implement three functions;
\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.

@@

>>>>

The translator is developed as a parser for the grammar
described in $\S$\ref{sec-trans}. 
The learner and checker module fully implemented 
the design in $\S$\ref{sec-learn} and $\S$\ref{sec-checker},
respectively.

%The implementation presented no interesting challenges. 
\com{
The learning and checking modules are developed to allow
for customized extensibility. In order to verify a configuration file
against a new type of error, a user only needs to provide a new type
that is an instance of the \textit{Attribute} typeclass (\ie, define some
functions over that type). 
In particular, for each type of error the users
wish to detect, they must implement three functions;
\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.}

@@

To verify errors,
our prototype follows three functions, 
\lstinline{learn}, \lstinline{merge}, and \lstinline{check},
to learn the rules.
